% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring

%------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\name{Sujeethan Vigneswaran}
\address{  
\href{mailto:sujeethan.vigneswaran@gmail.com}{sujeethan.vigneswaran@gmail.com}  
\\ 
\href{http://www.sujeethanvigneswaran.com}{Website} 
\\
\href{https://www.linkedin.com/in/sujeethan-vigneswaran/}{LinkedIn}
\\
\href{https://github.com/itssujee}{GitHub}
}

\begin{document}

%------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Cloud Systems Engineer}{May 2022 - December 2022}{Replicant}{San Francisco, CA}
\item Developed and implemented an innovative auto-scaling strategy to reduce cloud costs by \$300K annually, while simultaneously improving the customer experience through improved availability and performance.
\item Implemented a cost optimization program through developing cloud cost monitoring dashboards, resulting in a 20\% reduction in overall cloud costs for software developers, NLP scientists, and ML engineers.
\item Developed and executed a comprehensive testing plan to identify and prevent false-positive alerts, resulting in a 95\% reduction in erroneous on-call page notifications.
\end{rSubsection}

\begin{rSubsection}{Site Reliability Engineer}{January 2021 - December 2021}{Loblaw Digital \& Loblaw Companies Limited}{Toronto, ON}
\item Designed Kubernetes namespace monitoring dashboards that provided actionable insights leading to a 15\% decrease in unnecessary resource usage, resulting in an annual savings of \$200K.
\item Developed and implemented a cloud-based licensing automation system that cut licensing fees by \$120K annually, resulting in a 20\% cost reduction for the company.
\item Developed Terraform modules to enable developers to host web applications on Google Cloud, reducing deployment time by 90\% and increasing resource utilization efficiency by 20\%.
\end{rSubsection}

\begin{rSubsection}{Product Manager}{January 2020 - December 2020}{Loblaw Digital}{Toronto, ON}
\item Developed and executed a comprehensive go-to-market strategy for the 2022 PC Optimum Points Days Event, resulting in a week-long revenue of \$1.3B and an increase of 25\% in user engagement.
\item Created detailed user stories for Front-end, Back-end, Analytics, and QA development for the event which was experienced by over 18 million users. Decreased development time by 10\% through efficient collaboration with cross-functional teams.
\item Designed an A/B test to evaluate the impact of time-urgency on user experience and buying habits during the event. Improved conversion rates by 30\%, enhancing overall customer satisfaction.
\end{rSubsection}

\begin{rSubsection}{Big Data Software Engineer}{September 2019 - December 2019}{DRVN Intelligence}{Toronto, ON}
\item Developed an innovative system architecture for a digital media advertising platform, resulting in a 80\% reduction in deployment time and enabled customer acquisition.
\item Designed and implemented ETL pipelines in Apache Airflow \& Beam for multiple big data projects, resulting in faster data processing times by up to 40\%, improved data quality by 25\%, and reduced costs by \$500K annually.
\item Enabled the successful acquisition of Google Cloud Engineer Partner status by passing both Google Cloud Professional Data Engineer and Google Cloud Professional Cloud Architect certifications, resulting in a 95\% increase in business opportunities.
\end{rSubsection}

\end{rSection}

%------------------------------------------------------------------------
%	LEADERSHIP SECTION
%------------------------------------------------------------------------

% \begin{rSection}{Leadership Experience}

% {\bf Founder at \href{www.ladygodivapatches.com}{www.LadyGodivaPatches.com} } \\ 
% Designed, produced, and sold coverall patches (Canadian Engineering tradition) to the Canadian engineering community in 6 provinces and over 30 cities generating a return of investment of 300\%.

% {\bf \href{https://thestarfish.ca/journal/2018/06/2018-sftop25-finalist-sujeethan-vigneswaran-2}{Top 25 Environmentalists Under 25 in Canada}  } \\
% Nationally recognized by the Starfish Canada as one of the top 25 under 25 environmentalists for his work coordinating the restoration and environmental stewardship program in the Rouge National Urban Park.

% \end{rSection}

%------------------------------------------------------------------------
%	EDUCATION SECTION
%------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf University of Waterloo, Faculty of Engineering} \hfill {Waterloo, ON} \\
BASc in Environmental Engineering \& Minor in Management Engineering \\
Relevant Courses: Digital Computation, Statistics, Operations Management, Introduction to Complex Systems
\\
Capstone Project: Genetic Algorithm Optimization of EV-Charging Infrastructure Locations along Highway 401. 

\end{rSection}

%------------------------------------------------------------------------
%	SKILLS SECTION
%------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Product & Experimentation, GTM Strategy, Data Analytics \& Insights, User Interviews \\
Certificates & Google Cloud Professional Data Engineer \& Professional Cloud Architect\\
Technology & Docker, Kubernetes, Terraform, Linux, Python, SQL, Go, PagerDuty, JIRA 

\end{tabular}

\end{rSection}

\end{document}


